Transparent Changes

### 2022-05-03 thesis/methods.Rmd
Add appendices

The work presented in this thesis was preregistered before the start of the project on the [Open Science Framework](https://osf.io/3am4s) [@foster2017], following the 'Inclusive Systematic Review Registration Form' [@akker2020]. Any deviations from the preregistration are indicated in the 'Transparent Changes' document (Appendix A). Major deviations will also be explicitly stated within the methods section. All data and code of this research project can be found on [GitHub](https://www.github.com/smnnlt/vo2max-processing).

@@

The review was performed in accordance to the PRISMA extension for Scoping reviews [@tricco2018]. Appendix B contains the corresponding reporting checklist.

@@

The abstracts from the articles included in the random sample were blinded for scanning. This meant removing any further information not relevant for the screening---such as authors or journal---leaving only the title, abstract and an ID of the article (see Appendix C for an example). Two researchers independently scanned the abstracts to filter those that matched one of the exclusion criteria shown in Table 3. When the screeners disagreed in their assessments, they resolved the conflict by discussion.

>>>>

The work presented in this thesis was preregistered before the start of the project on the [Open Science Framework](https://osf.io/3am4s) [@foster2017], following the 'Inclusive Systematic Review Registration Form' [@akker2020]. Any deviations from the preregistration are indicated in the 'Transparent Changes' document (Appendix A.1). Major deviations will also be explicitly stated within the methods section. All data and code of this research project can be found on [GitHub](https://www.github.com/smnnlt/vo2max-processing).

I conducted all analyses using R Version 4.1.2 [@rcoreteam2022]. The thesis was entirely written in R Markdown Version 1.1 [@allaire2022]. The attached packages and default settings are documented in Appendix A.4.

@@

The review was performed in accordance to the PRISMA extension for Scoping reviews [@tricco2018]. Appendix A.2 contains the corresponding reporting checklist.

@@

The abstracts from the articles included in the random sample were blinded for scanning. This meant removing any further information not relevant for the screening---such as authors or journal---leaving only the title, abstract and an ID of the article (see Appendix A.3 for an example). Two researchers independently scanned the abstracts to filter those that matched one of the exclusion criteria shown in Table 3. When the screeners disagreed in their assessments, they resolved the conflict by discussion.

### 2022-05-03 transparent_changes.Rmd
Add appendices

---
title: "Transparent Changes"
author: Simon Nolte
output: 
  pdf_document: 
    latex_engine: xelatex
mainfont: Arial
urlcolor: blue
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

# Supplement to the project 'Data Processing Strategies to Determine Maximum Oxygen Uptake: A Systematic Scoping Review and Experimental Comparison'

@@

## Major Changes

### Number of exercise tests for comparison

@@

## Minor Changes

>>>>

---
title: ''
output: pdf_document
bibliography: references.bib
---

@@

### Major Changes

#### Number of exercise tests for comparison

@@

### Minor Changes
